---
output: 
  pdf_document:
    keep_tex: true
---

| | Program Level | Issue Level | 
|:--------|:--------------------------------------------|:--------------------------------------------|
|Policy Ends | How **comprehensive** is the **scope** of issues addressed? | What are the **specific requirements (i.e. policy settings)** on each issues? (e.g. the specific size of stream buffer zones) |
|Policy Means| In aggregate, across all issues, how **prescriptive** is each regulation? To what extent (e.g. on what portion of issues) are there mandatory and substantive thresholds? | 1. How **prescriptive** is each requirement? 2. How are they enforeced?*|

*Beyond the scope of this paper




```{r FSC-SFI-data, include=FALSE}
source(here::here("setup.R"))
load(here("data/SFIvFSC.Rdata"))
zeros <- issues %>%
  ungroup() %>% 
  select(pattern)  %>% 
  distinct()

zeros2 <- tibble(pattern = c("Downward parallell", "Downward divergence", "Opposing convergence"))

zeros %<>% full_join(zeros2) %>% 
  mutate(n = 0)
  
```

```{r 2010}
Issues <- issues %>% filter(Year == 2010) %>% group_by(pattern)  %>% select(pattern, Issue) %>% distinct() %>% mutate(issues = paste(Issue, collapse = ": ")) %>% group_by(pattern, issues) %>% tally() %>% arrange(-n) 

Issues %<>% full_join(filter(zeros, !pattern %in% Issues$pattern))

```


\begin{figure}
\caption{}
\end{figure}

2010

| | Converging | Parallell | Diverging |
|:----|:----:|:----:|:----:|
| Increasing | `r Issues$n[which(Issues$pattern == "Upward convergence")]`  | `r Issues$n[which(Issues$pattern == "Upward parallell")]`   | `r Issues$n[which(Issues$pattern == "Upward divergence")]`  |
| Opposing or Eqilibrium | `r Issues$n[which(Issues$pattern == "Opposing convergence")]` | `r Issues$n[which(Issues$pattern == "Equilibrium")]` | `r Issues$n[which(Issues$pattern == "Opposing divergence")]` |
| Decreasing | `r Issues$n[which(Issues$pattern == "Downward convergence")]` | `r Issues$n[which(Issues$pattern == "Downward parallell")]` | `r Issues$n[which(Issues$pattern == "Downward divergence")]` |


```{r 2015}
# Table
Issues <- issues %>% filter(Year == 2015) %>% group_by(pattern)  %>% select(pattern, Issue) %>% distinct() %>% mutate(issues = paste(Issue, collapse = ": ")) %>% group_by(pattern, issues) %>% tally() %>% arrange(-n)

Issues %<>% full_join(filter(zeros, !pattern %in% Issues$pattern))

```

2015

|  | Converging | Parallell | Diverging |
|:----|:----:|:----:|:----:|
| Increasing | `r Issues$n[which(Issues$pattern == "Upward convergence")]` | `r Issues$n[which(Issues$pattern == "Upward parallell")]` | `r Issues$n[which(Issues$pattern == "Upward divergence")]` |
| Opposing or Eqilibrium | `r Issues$n[which(Issues$pattern == "Opposing convergence")]` | `r Issues$n[which(Issues$pattern == "Equilibrium")]` | `r Issues$n[which(Issues$pattern == "Opposing divergence")]` |
| Decreasing | `r Issues$n[which(Issues$pattern == "Downward convergence")]` | `r Issues$n[which(Issues$pattern == "Downward parallell")]` | `r Issues$n[which(Issues$pattern == "Downward divergence")]` |


