---
output: 
  pdf_document
---



```{r FSC-SFI-data, include=FALSE}
source(here::here("setup.R"))
load(here("data/SFIvFSC.Rdata"))
zeros <- issues %>%
  ungroup() %>% 
  select(pattern)  %>% 
  distinct()

zeros2 <- tibble(pattern = c("Downward parallell", "Downward divergence", "Opposing convergence"))

zeros %<>% full_join(zeros2) %>% 
  mutate(n = 0)
  
```

```{r 2010}
Issues <- issues %>% filter(Year == 2010) %>% group_by(pattern)  %>% select(pattern, Issue) %>% distinct() %>% mutate(issues = paste(Issue, collapse = ": ")) %>% group_by(pattern, issues) %>% tally() %>% arrange(-n) 

Issues %<>% full_join(filter(zeros, !pattern %in% Issues$pattern))

```





\centerline{2010}

| | Converging | Parallell | Diverging |
|:----|:----:|:----:|:----:|
| Increasing | `r Issues$n[which(Issues$pattern == "Upward convergence")]`  | `r Issues$n[which(Issues$pattern == "Upward parallell")]`   | `r Issues$n[which(Issues$pattern == "Upward divergence")]`  |
| Opposing or Eqilibrium | `r Issues$n[which(Issues$pattern == "Opposing convergence")]` | `r Issues$n[which(Issues$pattern == "Equilibrium")]` | `r Issues$n[which(Issues$pattern == "Opposing divergence")]` |
| Decreasing | `r Issues$n[which(Issues$pattern == "Downward convergence")]` | `r Issues$n[which(Issues$pattern == "Downward parallell")]` | `r Issues$n[which(Issues$pattern == "Downward divergence")]` |


```{r 2015}
# Table
Issues <- issues %>% filter(Year == 2015) %>% group_by(pattern)  %>% select(pattern, Issue) %>% distinct() %>% mutate(issues = paste(Issue, collapse = ": ")) %>% group_by(pattern, issues) %>% tally() %>% arrange(-n)

Issues %<>% full_join(filter(zeros, !pattern %in% Issues$pattern))

```

\centerline{2015}

|  | Converging | Parallell | Diverging |
|:----|:----:|:----:|:----:|
| Increasing | `r Issues$n[which(Issues$pattern == "Upward convergence")]` | `r Issues$n[which(Issues$pattern == "Upward parallell")]` | `r Issues$n[which(Issues$pattern == "Upward divergence")]` |
| Opposing or Eqilibrium | `r Issues$n[which(Issues$pattern == "Opposing convergence")]` | `r Issues$n[which(Issues$pattern == "Equilibrium")]` | `r Issues$n[which(Issues$pattern == "Opposing divergence")]` |
| Decreasing | `r Issues$n[which(Issues$pattern == "Downward convergence")]` | `r Issues$n[which(Issues$pattern == "Downward parallell")]` | `r Issues$n[which(Issues$pattern == "Downward divergence")]` |

