---
title: "Untitled"
author: "Devin Judge-Lord"
date: "2/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# new feature request 
A font `family` argument for `shape` in `geom_point` (like `family` in `geom_text`) could vastly expand available glyphs by allowing Unicode characters missing from the default font. Alternatively, `base_family` with complete themes could be used when Unicode is supplied to the `shape` scale. 

The example requires the "Calibri" font:

```{r}
library(extrafont)
font_import()
glyphs <- c('\u2197', '\u2198')
p <- ggplot(NULL, aes(x = 0, y=c(1,2), color = glyphs))
```

`geom_text` plots Unicode symbols, but not in the legend. 
```{r}
p +
  geom_text(aes(label = glyphs), family = "Calibri")
```

`geom_point` seems like the right way to plot Unicode glyphs, if it and/or `scale_shape` had a `family` argument like this:

```{r}
p +
  geom_point( aes(shape = glyphs), family = "Calibri") +
  scale_shape_manual(values = glyphs)
```

Or if `base_family` applied to Unicode supplied to the `shape` scale:
```{r}
p + 
  geom_point(aes(shape = glyphs) ) +
  scale_shape_manual(values = glyphs) + 
  theme_gray(base_family = "Calibri") 
```
